Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-05 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:05	18:28:30	(Wed 5.Aug)

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows.eps}%
\caption{Typical window responses for a robust MVDR. The dashed red line is the response of an unsteered rectangular window on the full array. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight. Full opening angle. Parameters. }\label{mvdr_selected_windows}
\end{figure*}

>>>>

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR. A 40x40 pixel group from shadow, highlight and speckle were chose, and the window responses from each pixel plotted on top of each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe level of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight. Full opening angle. Parameters. }\label{mvdr_selected_windows}
\end{figure*}
